\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}
\begin{document}

\begin{flushleft}
\textbf{Ashutosh Kumbhar} \\
Tempe, Arizona, USA \\
+1 623-698-7433 \\
akumbha3@asu.edu \\
https://ashutosh.us \\
github.com/2727-ask \\
\today
\end{flushleft}

\vspace{0.5em}
\textbf{Hiring Manager} \\
Radian

\vspace{1em}

Dear Hiring Manager,

I am writing to express my interest in the Software Engineering GenAI Summer Intern position at Radian. As a Master's student in Software Engineering at Arizona State University with a strong foundation in full-stack development, machine learning, and cloud technologies, I am eager to apply my skills and grow as a software engineer at Radian.

During my time at Western Union, I contributed to the development and maintenance of the POS retail application, utilizing technologies such as Angular 14, Java, and Docker to drive improvements that boosted developer efficiency by 70% and increased revenue by 15%. I have experience with agile development methodologies and am skilled in coding, debugging, and working collaboratively in cross-functional teams.

In addition, I have developed AI-powered applications, such as a cryptocurrency tracker leveraging Firebase and Flutter, and have a strong interest in technologies like TensorFlow, PyTorch, and OpenAI. My experience with cloud platforms, including AWS and GCP, aligns well with Radian’s cloud-based infrastructure.

Radian’s commitment to diversity, innovation, and flexible work aligns with my values, and I am excited about the opportunity to contribute to impactful projects with the GenAI team. I am confident that my problem-solving skills, passion for AI, and ability to quickly adapt to new technologies will make me a strong asset to your team.

Thank you for considering my application. I look forward to the opportunity to further discuss how my skills can contribute to the success of Radian.

Sincerely, \\
Ashutosh Kumbhar

\end{document}
