%-------------------------
% Resume in Latex
% Author : Ashutosh Kumbhar
% Based off of: https://github.com/2727-ask
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}


\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}


\begin{center}
    \textbf{\Huge \scshape Ashutosh Kumbhar} \\ \vspace{1pt}
    \small +1 6236987433 $|$ \href{mailto:akumbha3@asu.edu}{\underline{akumbha3@asu.edu}} $|$ 
    \href{https://github.com/2727-ask}{\underline{github.com/2727-ask}} $|$
    \href{https://ashutosh.us}{\underline{ashutosh.us}} $|$
    \small Tempe, AZ, USA
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Arizona State University}{Tempe, AZ}
      {Master of Software Engineering}{Aug. 2024 -- May 2026}
    \resumeSubheading
      {Savitribai Phule University}{Pune, India}
      {Bachelor of Engineering in Computer Science}{Aug. 2019 -- May 2023}
  \resumeSubHeadingListEnd
  
%-----------PROGRAMMING SKILLS-----------

\section{Technical Skills}
\resumeSubHeadingListStart
  \resumeSubItem{\textbf{Languages:} C, C++, Java, Python, Dart, Go, JavaScript, Rust, HTML5.}
  \resumeSubItem{\textbf{Frameworks:} Angular, ReactJS, Vue.js, Django, Flask, Express.js, Electron.js, Tauri, Flutter, Ionic, Spring Boot.}
  \resumeSubItem{\textbf{Technologies:} Docker, Kubernetes, REST, JSON, TypeScript, GenAI, Selenium, BS4, FastAPI.}
  \resumeSubItem{\textbf{Developer Tools:} Git, GraphQL, Docker, Google Cloud Platform, Amazon Web Services, Firecracker, Kubernetes, Redis, Agile, SCRUM, Linux, JIRA.}
  \resumeSubItem{\textbf{Database:} MongoDB, PostgreSQL, Oracle, MySQL, Firebase, SQLite}
  \resumeSubItem{\textbf{Cloud Infrastructure:} Cloud Storage Infrastructure, Virtualization, Data Platform Tools, Cloud Storage Automation, Cloud Infrastructure Troubleshooting.}
  \resumeSubItem{\textbf{Distributed Systems:} Distributed Systems, Data Structures & Algorithms, Virtualization, Container & Cluster Management, Microservices, Schedulers (LSF, SLURM).}
  \resumeSubItem{\textbf{Programming Concepts:} Linear Algebra, Numerical Methods, Operating Systems (memory/resource management), Scheduling and Process Control, Object-Oriented Programming (OOP), Debugging Tools.}
  \resumeSubItem{\textbf{Scripting & Automation:} Unix/Shell Scripting, Configuration Automation (Ansible), Automation/Scripting.}
  \resumeSubItem{\textbf{Data Technologies:} Kafka, ELK, Cassandra, Spark, Data Science, Data Engineering, Open Source Data Science Tools, Open Source Libraries.}
  \resumeSubItem{\textbf{Performance & Diagnostics:} Application Tracing, Analysis, Modeling, Diagnostics, Performance Tuning, Debugging.}
  \resumeSubItem{\textbf{Version Control & Collaboration:} Git, GitLab, Perforce.}
\resumeSubHeadingListEnd
%-------------------------------------------

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Software Engineer - Western Union}{May. 2023 -- Aug 2024}
      {Western Union}{Full-Time}
      \resumeItemListStart
        \resumeItem{Contributed to developing and maintaining the Western Union POS retail application, ensuring seamless
functionality and performance.}
        \resumeItem{Developed \textbf{Point Of Sale Development Utility}, which boosted developer \textbf{efficiency by 70\%}}
        \resumeItem{Collaborated in the migration of \textbf{WUPOS} from Apache Tapestry to Angular 14, and Microservices-based architecture resulting in \textbf{a 15\% increase in revenue}, significant improvements in both agent and user experience, and \textbf{expanded market share} through modernized front-end architecture.}
        \resumeItem{Executed a Test-Driven Development (TDD) strategy within teams using the \textbf{Playwright} framework.}
      \resumeItemListEnd

     \resumeSubheading
      {Software Engineer Intern - Amazon Web Services}{January 2021 -- May 2023}
      {LinkCode Technologies}{Internship}
      \resumeItemListStart
        \resumeItem{Designed the architecture for the LinkCode LMS, driving the organization's digital transformation and resulting in a \textbf{35\% increase in revenue}.}
        \resumeItem{Managed a team of \textbf{10 developers}, overseeing the collective development and implementation of the software.}
        \resumeItem{Migrated the entire infrastructure to a server-less architecture using AWS \textbf{Lambda}, enhancing scalability and cost-efficiency.}
        \resumeItem{Implemented \textbf{Web-RTC} for video conferencing, improving real-time communication capabilities.}
        \resumeItem{Established CI/CD pipelines with Jenkins, optimizing development workflows and deployment processes.}
      \resumeItemListEnd
      
      \resumeSubheading
      {Full-Stack Development Intern}{April 2020 -- September 2020}
      {Aitheon}{Internship}
      \resumeItemListStart
        \resumeItem{Created a \textbf{no-code} application development platform using Visual Studio Web, Node.js, Node-RED, and Vue.js, enabling users to create applications without traditional coding.}
        \resumeItem{Development of \textbf{IoT} applications leveraging Robot Operating Systems, NVIDIA Jetson Nano, and Code-Studio.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
  {\textbf{Online Compiler Web IDE} $|$ \emph{Docker, Kubernetes, Redis, Node.js, Angular, Nginx}}{}
\resumeItemListStart
  \resumeItem{Developed a cloud-based platform supporting over 10+ programming languages, enabling software developers and students to perform heavy computation without local hardware.}
  \resumeItem{Collaborated with a team to design a highly scalable architecture leveraging containerization technologies like Docker and Kubernetes.}
\resumeItemListEnd

\resumeProjectHeading
  {\textbf{Diagnostic Center Resource Management System} $|$ \emph{Vue.js, Electron.js, Firebase, Google Cloud}}{}
\resumeItemListStart
  \resumeItem{Designed and implemented a web application to manage resources and patient data, boosting productivity by \textbf{80\%} for the Unique Diagnostic Center.}
  \resumeItem{Integrated Firebase for real-time data synchronization and GCP for cloud-based resource scaling, improving performance and availability.}
\resumeItemListEnd

\resumeProjectHeading
  {\textbf{Instagram Video Scraper + Auto YouTube Shorts Uploader} $|$ \emph{Selenium, BS4, Flutter, FastAPI, GenAI}}{}
\resumeItemListStart
  \resumeItem{Developed a Python script to automatically scrape Instagram videos while scrolling through reels using Selenium and BeautifulSoup.}
  \resumeItem{Automated the uploading of videos to YouTube, including generating video tags and metadata using GenAI for improved search visibility.}
\resumeItemListEnd
      


          
    \resumeSubHeadingListEnd





%

\end{document}
