\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}
\begin{document}

\begin{flushleft}
\textbf{Ashutosh Kumbhar} \\
Tempe, Arizona, USA \\
+1 623-698-7433 \\
akumbha3@asu.edu \\
https://ashutosh.us \\
github.com/2727-ask \\
\today
\end{flushleft}
\vspace{0.5em}
\textbf{Hiring Manager} \\
NVIDIA \\
\vspace{1em}

Dear Hiring Manager,

I am excited to apply for the Software Engineering Internship at NVIDIA for the Summer 2025 program. Currently pursuing a Master’s in Software Engineering at Arizona State University, I am passionate about leveraging my skills in C++, Python, and cloud technologies to contribute to the cutting-edge work NVIDIA is doing in AI, robotics, and digital twins.

With over a year of experience in software development, I have worked on diverse projects that align with your team's goals. At Western Union, I contributed to the migration of a major POS system to Angular 14, improving both revenue and user experience. Additionally, my work in deploying cloud-based microservices with Kubernetes at MindsClik Digital Solutions equipped me with deep insights into containerization and cloud infrastructure—skills that are essential for this internship. 

I am particularly drawn to NVIDIA’s mission of tackling complex challenges in industries like gaming, healthcare, and climate change, and I am eager to bring my expertise in distributed systems, automation scripting, and debugging to your teams. My academic focus on data structures, algorithms, and system-level programming, paired with hands-on experience using Git, Kubernetes, and Docker, makes me well-suited for this role.

I look forward to the opportunity to contribute to NVIDIA’s innovative projects while expanding my knowledge of high-performance computing and artificial intelligence. Thank you for considering my application, and I am excited about the chance to discuss how my skills align with the needs of your team.

Sincerely, \\
Ashutosh Kumbhar

\end{document}
