\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}
\begin{document}

\begin{flushleft}
\textbf{Ashutosh Kumbhar} \\
Tempe, Arizona, USA \\
+1 623-698-7433 \\
akumbha3@asu.edu \\
linkedin.com/in/ashutosh-kumbhar \\
github.com/2727-ask \\
\today
\end{flushleft}

\vspace{0.5em}
\textbf{Hiring Manager} \\
FOX Sports Cincinnati \\

\vspace{1em}

Dear Hiring Manager,

I am writing to express my interest in the Software Developer Internship at FOX Sports Cincinnati. As a Master's student in Software Engineering at Arizona State University, with a strong background in full-stack development and experience in building high-performance digital products, I am eager to contribute to your innovative development team. FOX Sports' commitment to creating world-class digital products for millions of sports fans resonates with my passion for software development and sports.

Throughout my career, I have developed a wide range of skills that align closely with the responsibilities of this internship. In my previous role at Western Union, I contributed to the development and modernization of the POS retail application, significantly improving agent and user experience by migrating to Angular 14. I also have experience developing mobile applications using Flutter, such as the real-time cryptocurrency tracker that I built for cross-platform performance and scalability. Furthermore, my knowledge of Docker, Kubernetes, and cloud-based technologies like AWS and GCP aligns with your focus on leveraging modern technologies for building digital platforms.

At FOX Cincinnati, I look forward to learning from industry-leading professionals and contributing to product brainstorming sessions, developing features that will impact millions of users. Your dynamic and creative culture, combined with the opportunity to grow in the software development lifecycle, excites me. I am committed to contributing clean, optimized, and well-tested code while enhancing my skills and embracing new challenges.

I would welcome the opportunity to further discuss how my background, skills, and experiences align with the needs of your team. Thank you for considering my application. I look forward to the possibility of contributing to your continued success.

Sincerely, \\
Ashutosh Kumbhar

\end{document}
