\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}

\begin{document}

\begin{flushleft}
\textbf{Ashutosh Kumbhar} \\
Tempe, Arizona, USA \\
+1 623-698-7433 \\
akumbha3@asu.edu \\
https://ashutosh.us \\
github.com/2727-ask \\
\today
\end{flushleft}

\vspace{0.5em}

\textbf{Hiring Manager} \\
School of Earth and Space Exploration \\

\vspace{1em}

Dear Hiring Manager,

I am writing to express my enthusiasm for the Database Developer role at the School of Earth and Space Exploration. As a master's student in Software Engineering at Arizona State University with a strong foundation in database management and software development, I am eager to contribute to your mission of integrating research and education in innovative ways.

In my recent role at Western Union, I developed a Point of Sale Development Utility that enhanced developer efficiency by 70\% and contributed to a migration project that modernized the application architecture, resulting in a 15\% revenue increase. My experience aligns with your needs for MySQL development and ETL processes, as I have implemented robust database solutions using tools like MySQL, PostgreSQL, and MongoDB. Additionally, I have utilized Python extensively for data handling and automation, including developing scalable backend services and integrating APIs.

At MindsClik Digital Solutions, I deployed a microservice infrastructure on Google Cloud Platform using Kubernetes, showcasing my expertise in cloud-based solutions and data-driven applications. My familiarity with JSON and Google Forms positions me to streamline data ingestion processes, a key requirement of this role. Furthermore, my projects, such as building an Online Compiler Web IDE, demonstrate my ability to design and implement efficient database CRUD operations and scalable architectures.

The School of Earth and Space Exploration's dedication to transdisciplinary research and education resonates deeply with my aspirations to apply technical expertise in meaningful, impactful settings. I am particularly excited about contributing to the L’Space team’s initiatives and supporting the broader goals of your department.

I am confident that my technical skills, coupled with my passion for innovation and problem-solving, make me a strong fit for this position. I look forward to the opportunity to discuss how I can contribute to your team.

Sincerely, \\
Ashutosh Kumbhar

\end{document}
