\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}

\begin{document}

\begin{flushleft}
\textbf{Ashutosh Kumbhar} \\
Tempe, Arizona, USA \\
+1 623-698-7433 \\
akumbha3@asu.edu \\
https://ashutosh.us \\
github.com/2727-ask \\
\today
\end{flushleft}

\vspace{0.5em}

\textbf{Hiring Manager} \\
ASU Technology Assistant \\

\vspace{1em}

Dear Hiring Manager, \\

I am writing to express my interest in the Technology Assistant position at ASU. As a Master’s student in Software Engineering at Arizona State University with a strong foundation in IT support and software development, I am eager to contribute my technical expertise and problem-solving skills to support the university’s technological initiatives. 

In my professional experience as a Software Developer at Western Union, I enhanced team efficiency by 70\% through the development of a Point of Sale Development Utility and contributed to a successful front-end migration that improved user experience and increased revenue by 15\%. My academic projects, such as developing a cloud-based Online Compiler Web IDE and a Diagnostic Center Resource Management System, demonstrate my ability to manage complex technical challenges, leverage cloud platforms, and deliver scalable solutions. 

I am particularly drawn to ASU’s mission of innovation and community engagement. My proficiency with Windows, MacOS, Office 365 tools like Power Automate, and hands-on experience with troubleshooting and configuring hardware/software make me well-suited to assist with IT support tasks. Furthermore, my organizational skills and commitment to detail align with the responsibilities of maintaining IT assets and supporting athletic events.

I am excited about the opportunity to contribute to ASU's technological operations while advancing my own expertise in a collaborative environment. I would welcome the chance to discuss how my technical skills and proactive approach can add value to the team.

Thank you for considering my application. I look forward to the opportunity to discuss my qualifications further.

Sincerely, \\
Ashutosh Kumbhar

\end{document}
