\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}
\begin{document}
\begin{flushleft}
\textbf{Ashutosh Kumbhar} \\
Tempe, Arizona, USA \\
+1 623-698-7433 \\
akumbha3@asu.edu \\
linkedin.com/in/ashutosh-kumbhar \\
github.com/2727-ask \\
\today
\end{flushleft}
\vspace{0.5em}
\textbf{Hiring Manager} \\
Cozii Technologies \\
\vspace{1em}

Dear Hiring Manager,

I am writing to express my interest in the Software Developer Intern position at Cozii Technologies. As a passionate software engineer with a strong foundation in full-stack development, I am eager to contribute my skills and enthusiasm to a dynamic team working at the intersection of technology and the real estate industry.

Throughout my experience, I have demonstrated a commitment to building high-quality, scalable applications. While interning at Aitheon, I developed a no-code application development platform that empowered users to create applications without traditional coding, showcasing my ability to think creatively and solve real-world problems. At Western Union, I contributed to the migration of a legacy application to Angular, resulting in a 15% increase in revenue, which highlights my expertise in modern web technologies and frameworks such as Angular and React.

I am particularly excited about the opportunity to work with Cozii Technologies, given your focus on revolutionizing the property management industry through innovative technological solutions. My experience working with JavaScript and modern frameworks such as React, Vue, and Angular aligns well with the technologies used at Cozii. Additionally, I have a strong commitment to maintaining high standards for code quality, as demonstrated in my previous roles where I executed Test-Driven Development (TDD) and ensured efficient debugging processes.

I am confident that my technical skills, combined with my passion for technology and problem-solving, make me a strong candidate for this internship. I would welcome the opportunity to further discuss how I can contribute to your team and the impactful projects at Cozii Technologies.

Sincerely, \\
Ashutosh Kumbhar
\end{document}
