\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}
\begin{document}

\begin{flushleft}
\textbf{Ashutosh Kumbhar} \\
Tempe, Arizona, USA \\
+1 623-698-7433 \\
akumbha3@asu.edu \\
https://ashutosh.us \\
github.com/2727-ask \\
\today
\end{flushleft}

\vspace{0.5em}

\textbf{Hiring Manager} \\
\textbf{Arizona State University} \\

\vspace{1em}

Dear Hiring Manager,

I am excited to apply for the Technology Assistant position at Arizona State University. As a Master’s student in Software Engineering at ASU with extensive experience in IT support and software development, I am eager to contribute my technical expertise to enhance your department’s operational efficiency.

Throughout my career, I have honed my skills in hardware and software support, configuration, and troubleshooting. At Western Union, I developed a Point of Sale Development Utility that improved developer efficiency by 70\%, and at LinkCode Technologies, I led a team of 10 to migrate infrastructure to serverless architectures, increasing scalability and cost-efficiency. My experience with desktops, laptops, and mobile devices, combined with my hands-on proficiency in Windows 10 and macOS, aligns closely with the requirements of this role.

My familiarity with the Office 365 environment, particularly Power Automate, Power Apps, and PowerBI, equips me to handle diverse IT tasks and small application development projects. I excel at structured problem-solving and have a proven track record of managing IT assets and inventories. Additionally, my collaborative experience and communication skills enable me to provide tier 1 help desk support and troubleshoot efficiently in both onsite and remote settings.

I am particularly drawn to this role at ASU because of its dynamic nature, combining technical support with opportunities to contribute to athletic event operations. As someone who values teamwork and innovation, I am excited to bring my passion for technology and my commitment to excellence to this position.

I would welcome the opportunity to discuss how my background and skills align with the needs of your team. Thank you for considering my application. I look forward to the possibility of contributing to ASU’s success.

Sincerely, \\
Ashutosh Kumbhar

\end{document}
