\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}
\begin{document}

\begin{flushleft}
\textbf{Ashutosh Kumbhar} \\
Tempe, Arizona, USA \\
+1 623-698-7433 \\
akumbha3@asu.edu \\
https://ashutosh.us \\
github.com/2727-ask \\
\today
\end{flushleft}

\vspace{0.5em}

\textbf{Hiring Manager} \\
Tesla \\

\vspace{1em}

Dear Hiring Manager,

I am excited to apply for the Software Engineer Intern position on the Update Systems team at Tesla for Summer 2025. As a current master’s student in Software Engineering at Arizona State University, with a robust foundation in software development and automation, I am eager to contribute to Tesla’s mission of accelerating the world’s transition to sustainable energy through innovative technology.

During my tenure as a Software Developer at Western Union, I developed a Point of Sale Development Utility, increasing developer efficiency by 70\%, and collaborated on migrating the WUPOS application to Angular 14, resulting in a 15\% revenue increase. These experiences honed my skills in full-stack development, system optimization, and cross-functional collaboration. Additionally, my projects, such as a cloud-based Online Compiler Web IDE leveraging Docker and Kubernetes, demonstrate my proficiency in creating scalable, automated infrastructures.

Tesla’s focus on over-the-air updates and its integration of hardware-in-the-loop (HIL) and software-in-the-loop (SIL) testing resonates with my passion for creating robust, automated validation systems. My expertise in Python, combined with a strong foundation in object-oriented design and algorithmic problem-solving, aligns with the requirements of this role. Furthermore, my experience in designing CI/CD pipelines and working in Agile environments ensures I can contribute effectively to maintaining and enhancing Tesla’s validation tools and frameworks.

I am particularly inspired by Tesla’s innovative approach to technology and its commitment to sustainability. Joining your team would allow me to leverage my technical skills while contributing to solutions that redefine customer experiences.

Thank you for considering my application. I am eager to bring my technical expertise, problem-solving abilities, and passion for innovation to Tesla. I welcome the opportunity to discuss how my skills align with your team’s needs and would appreciate the chance to contribute to Tesla’s impactful work.

Sincerely, \\
Ashutosh Kumbhar

\end{document}
