\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}

\begin{document}
\begin{flushleft}
\textbf{Ashutosh Kumbhar} \\
Tempe, Arizona, USA \\
+1 623-698-7433 \\
akumbha3@asu.edu \\
linkedin.com/in/ashutosh-kumbhar \\
github.com/2727-ask \\
\today
\end{flushleft}

\vspace{0.5em}

\textbf{Hiring Manager} \\
Protiviti \\

\vspace{1em}

Dear Hiring Manager,

I am excited to apply for the Technology Consulting Intern - 2025 position at Protiviti. As a Master’s candidate in Software Engineering at Arizona State University and a seasoned software developer with diverse industry experience, I am eager to bring my technical expertise and passion for innovation to Protiviti’s dynamic environment.

Over the past three years, I have cultivated a robust skill set through roles at Western Union, MindsClik Digital Solutions, and other organizations. Notably, I spearheaded the migration of a point-of-sale system at Western Union to Angular 14, boosting revenue by 15\% while enhancing user experience. My ability to integrate modern frameworks and implement Test-Driven Development (TDD) has consistently delivered scalable, efficient solutions. Furthermore, my experience with cloud technologies, including Kubernetes and GCP, positions me to address complex client challenges in technology consulting.

Protiviti’s mission to deliver innovative, risk-resilient solutions aligns with my commitment to leveraging technology for impactful problem-solving. I am particularly inspired by Protiviti's emphasis on applying critical thinking to diverse industries—a principle reflected in my academic and professional projects. For instance, I developed a cloud-based Online Compiler Web IDE that optimized resource management and enhanced collaborative development, demonstrating my capability to manage end-to-end technology solutions.

My technical proficiency spans programming languages such as Python, Java, and JavaScript, complemented by experience with SQL databases and tools like Power BI. My foundational knowledge of IT controls, cybersecurity, and process reengineering further equips me to navigate the multifaceted responsibilities of a Technology Consultant.

I am confident that my technical skills, coupled with my problem-solving acumen and collaborative mindset, make me an excellent fit for Protiviti’s Technology Consulting Internship. I welcome the opportunity to discuss how my experience and goals align with Protiviti’s vision. Thank you for considering my application.

Sincerely, \\
Ashutosh Kumbhar
\end{document}
