\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}
\begin{document}

\begin{flushleft}
\textbf{Ashutosh Kumbhar} \\
Tempe, Arizona, USA \\
+1 623-698-7433 \\
akumbha3@asu.edu \\
https://ashutosh.us \\
github.com/2727-ask \\
\today
\end{flushleft}

\vspace{0.5em}

\textbf{Hiring Manager} \\
C3.ai \\

\vspace{1em}

Dear Hiring Manager,

I am excited to apply for the Software Engineer Intern position at C3.ai for Summer 2025. As a Master’s student in Software Engineering at Arizona State University with a strong foundation in scalable system development, AI applications, and collaborative engineering, I am eager to contribute to your mission of accelerating digital transformation through enterprise AI solutions.

In my professional journey, I’ve developed impactful solutions such as a Point of Sale Development Utility at Western Union, which improved developer efficiency by 70\%, and led a seamless migration to Angular 14, increasing revenue by 15\%. At MindsClik Digital Solutions, I designed and deployed a white-labeled e-commerce solution and microservices architecture on Google Cloud Platform using Kubernetes. These experiences honed my skills in JavaScript, object-oriented programming, data structures, and scalable system design, aligning perfectly with C3.ai's requirements.

Your commitment to delivering prebuilt, high-value AI applications resonates with my passion for developing impactful AI-powered solutions. My recent project—an online compiler supporting over 10 programming languages—leveraged Docker and Kubernetes for scalability and cost optimization. This aligns closely with your mission of creating performant and scalable applications on the C3 AI Suite.

I am particularly drawn to C3.ai’s innovative culture and its emphasis on fostering intellectual growth. The opportunity to collaborate in an autonomous and empowering environment while tackling real-world challenges excites me. I am confident that my technical expertise and problem-solving abilities make me a strong fit for this role.

I look forward to the possibility of contributing to C3.ai's mission and would welcome the opportunity to discuss how my skills and experiences align with your needs. Thank you for considering my application.

Sincerely, \\
Ashutosh Kumbhar

\end{document}
