\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}

\begin{document}

\begin{flushleft}
\textbf{Ashutosh Kumbhar} \\
Tempe, Arizona, USA \\
+1 623-698-7433 \\
akumbha3@asu.edu \\
https://ashutosh.us \\
github.com/2727-ask \\
\today
\end{flushleft}

\vspace{0.5em}

\textbf{Hiring Manager} \\
Intuitive \\

\vspace{1em}

Dear Hiring Manager, \\

I am excited to apply for the Software Engineering Intern position within the Core Technologies Engineering (CTE) group at Intuitive. With a robust academic foundation in software engineering and hands-on experience spanning software development, virtualization, and embedded systems, I am eager to contribute to advancing the da Vinci emulator and hybrid hardware-in-the-loop systems.  

In my current Master’s program at Arizona State University and professional roles, I have honed my skills in Python, C++, and Linux environments—key technologies relevant to this role. As a Software Developer at Western Union, I spearheaded the migration of a Point of Sale (POS) system to Angular 14, yielding a 15\% revenue increase. Furthermore, I developed a POS utility tool that improved developer efficiency by 70\%, showcasing my ability to design impactful internal tools. My work with QEMU to optimize resource management for a cloud-based online compiler platform directly aligns with the emulator and virtualization focus at Intuitive.

What excites me most about Intuitive is its commitment to revolutionizing minimally invasive care through technology—a vision that resonates deeply with my passion for creating solutions that improve lives. The opportunity to collaborate with cross-disciplinary engineers on innovative projects, while learning and practicing Intuitive's development methodologies, aligns perfectly with my career aspirations.  

I am confident that my technical expertise, coupled with my proactive approach to problem-solving and passion for innovation, make me a strong fit for this internship. I welcome the opportunity to discuss how my skills and experiences align with Intuitive's goals. Thank you for considering my application. I look forward to the possibility of contributing to your team.  

Sincerely, \\
Ashutosh Kumbhar  

\end{document}
