\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}

\begin{document}

\begin{flushleft}
\textbf{Ashutosh Kumbhar} \\
Tempe, Arizona, USA \\
+1 623-698-7433 \\
akumbha3@asu.edu \\
\texttt{https://ashutosh.us} \\
\texttt{github.com/2727-ask} \\
\today
\end{flushleft}

\vspace{0.5em}

\textbf{Hiring Manager} \\
Moloco \\

\vspace{1em}

Dear Hiring Manager,

I am excited to apply for the \textbf{Software Engineer Intern} position at Moloco. As a Master's student in Software Engineering at Arizona State University, I have a strong background in \textbf{data structures, algorithms, and backend development}. With experience working on performance-driven projects and solving complex technical challenges, I am eager to contribute to Moloco’s mission of revolutionizing advertising through machine learning and data-driven insights.

During my time at \textbf{Western Union}, I contributed to the development and migration of a high-performance \textbf{POS retail application} from Apache Tapestry to Angular 14, increasing revenue by \textbf{15\%} and enhancing user experience. I also improved development efficiency by \textbf{70\%} through a custom-built POS Development Utility. These experiences helped sharpen my problem-solving and coding skills, which I am eager to apply in Moloco’s high-impact engineering environment.

Additionally, at \textbf{MindsClik Digital Solutions}, I deployed a scalable \textbf{microservices infrastructure} using \textbf{Google Cloud Platform} and Kubernetes, improving backend performance. My ability to optimize backend systems and develop server-side solutions was further demonstrated through my work on cloud-based platforms and developing REST APIs for system communication.

I am particularly drawn to Moloco’s use of \textbf{machine learning} to drive business success and its focus on creating value through intelligent, data-driven solutions. My experience in \textbf{backend development, API frameworks, and distributed systems} equips me to contribute effectively to your innovative projects, from enhancing scalability to implementing new features.

I am excited about the opportunity to work with Moloco’s talented team, learn from experienced mentors, and contribute to building impactful solutions. Thank you for your time and consideration.

Sincerely, \\
Ashutosh Kumbhar

\end{document}
