\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}

\begin{document}

\begin{flushleft}
\textbf{Ashutosh Kumbhar} \\
Tempe, Arizona, USA \\
+1 623-698-7433 \\
akumbha3@asu.edu \\
https://ashutosh.us \\
github.com/2727-ask \\
\today
\end{flushleft}

\vspace{0.5em}

\textbf{Hiring Manager} \\
Tanium \\

\vspace{1em}

Dear Hiring Manager,  

I am excited to apply for the Software Engineering Intern position at Tanium for Summer 2025. As a Master’s candidate in Software Engineering at Arizona State University with a strong foundation in building scalable software systems, I am eager to contribute to Tanium's mission of delivering real-time, autonomous endpoint management solutions.  

With over two years of professional experience, I have developed and optimized software solutions that drive efficiency and performance. At Western Union, I enhanced developer productivity by 70\% through a custom-built POS Development Utility and contributed to the migration of legacy systems to Angular, resulting in a 15\% revenue increase. My projects often intersect security and scalability—aligning with Tanium’s focus on reliable, cutting-edge B2B applications.  

I am particularly drawn to Tanium’s culture of innovation and collaboration. The opportunity to work on projects such as developing a visualization tool for privileges and roles or enhancing natural language parsing resonates with my passion for backend and full-stack development. My prior experiences, including leading a team to architect an LMS that increased revenue by 35\% and deploying microservice infrastructures on Kubernetes, prepare me to tackle complex challenges while learning and contributing in a dynamic environment.  

Beyond technical expertise, I value teamwork and continuous improvement. My experience working in Agile teams and mentoring peers equips me to collaborate effectively with Tanium’s diverse engineering community. The emphasis on delivering real-world solutions during the internship aligns with my goal of crafting impactful software.  

I am confident that my skills and drive make me a strong fit for this role. I look forward to the possibility of discussing how my background aligns with Tanium’s vision. Thank you for considering my application.  

Sincerely, \\
Ashutosh Kumbhar  

\end{document}
