\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}

\begin{document}

\begin{flushleft}
\textbf{Ashutosh Kumbhar} \\
Tempe, Arizona, USA \\
+1 623-698-7433 \\
akumbha3@asu.edu \\
https://ashutosh.us \\
github.com/2727-ask \\
\today
\end{flushleft}

\vspace{0.5em}

\textbf{Hiring Manager} \\
ASU \\

\vspace{1em}

Dear Hiring Manager,

I am excited to apply for the Research Aide position specializing in UI, DevOps, AWS, and Kubernetes/Docker at ASU. As a Master's student in Software Engineering at ASU with over three years of professional experience in full-stack and cloud-based development, I bring a robust skill set and a proven ability to deliver scalable and efficient software solutions.

During my tenure at Western Union, I spearheaded the migration of their POS system to a modern Angular-based architecture, resulting in a 15\% revenue increase and significantly improving user experience. At MindsClik Digital Solutions, I deployed a Kubernetes-managed microservice infrastructure on Google Cloud Platform, enhancing scalability and system reliability. Additionally, my role at LinkCode Technologies involved leading a team of 10 developers to transition to a serverless architecture using AWS Lambda, reducing costs and improving scalability.

ASU’s mission of innovation aligns with my passion for leveraging technology to address complex challenges. My projects, such as the development of a cloud-based online compiler utilizing Docker and Kubernetes, exemplify my dedication to creating scalable and efficient solutions. Additionally, my experience with object detection models and frameworks like TensorFlow and OpenCV positions me to contribute effectively to your AI-driven video stream processing system on AWS.

I am adept at RESTful API development, container orchestration, and CI/CD pipelines using tools like Jenkins and GitLab CI. My proficiency in Python, coupled with a strong foundation in deep learning and computer vision, aligns closely with the desired qualifications for this role.

I am eager to bring my expertise to ASU, contributing to cutting-edge research and development. I welcome the opportunity to discuss how my skills and experiences align with your team’s goals.

Sincerely, \\
Ashutosh Kumbhar

\end{document}
