\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}

\begin{document}

\begin{flushleft}
\textbf{Ashutosh Kumbhar} \\
Tempe, Arizona, USA \\
+1 623-698-7433 \\
akumbha3@asu.edu \\
\texttt{https://ashutosh.us} \\
\texttt{github.com/2727-ask} \\
\today
\end{flushleft}

\vspace{0.5em}

\textbf{Hiring Manager} \\
Verint \\

\vspace{1em}

Dear Hiring Manager,

I am excited to apply for the \textbf{Software Engineer Intern} position at Verint. As a Master's student in Software Engineering at Arizona State University with hands-on experience in \textbf{backend development, API frameworks, and enterprise software solutions}, I am eager to contribute to Verint’s mission of delivering cutting-edge CX automation and workforce productivity solutions. My background in \textbf{Java, cloud infrastructure, and Agile development} aligns well with the role's objectives.

At \textbf{Western Union}, I played a pivotal role in developing and maintaining the \textbf{POS retail application}, ensuring seamless performance. I contributed to the migration of WUPOS from Apache Tapestry to \textbf{Angular 14}, improving user experience and driving a \textbf{15\% increase in revenue}. Additionally, I developed a \textbf{POS Development Utility} that boosted developer efficiency by \textbf{70\%}. My strong foundation in \textbf{Test-Driven Development (TDD)} using Playwright has enabled me to write maintainable, high-quality code.

Beyond backend development, I have extensive experience in \textbf{debugging, troubleshooting, and resolving software issues}. At \textbf{MindsClik Digital Solutions}, I deployed an entire \textbf{microservices infrastructure} on \textbf{Google Cloud Platform} using Kubernetes and optimized backend services with \textbf{Node.js and RESTful APIs}. Furthermore, my work on the \textbf{Online Compiler Web IDE} involved integrating \textbf{Docker, Kubernetes, and Redis} to enable seamless multi-language execution.

I am particularly drawn to Verint’s focus on \textbf{enterprise application development, automation, and AI-driven solutions}. My proficiency in \textbf{Java, .NET, object-oriented design, and API development}, along with experience in \textbf{debugging, code reviews, and cross-functional team collaboration}, makes me a strong candidate for this role. Additionally, my ability to quickly adapt to new frameworks and methodologies aligns well with Verint’s innovative and fast-paced environment.

I am eager to bring my \textbf{problem-solving skills, backend expertise, and software quality assurance experience} to Verint. I would welcome the opportunity to further discuss how my skills and experiences align with your team’s goals. Thank you for your time and consideration.

Sincerely, \\
Ashutosh Kumbhar

\end{document}
