\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}

\begin{document}

\begin{flushleft}
\textbf{Ashutosh Kumbhar} \\
Tempe, Arizona, USA \\
+1 623-698-7433 \\
akumbha3@asu.edu \\
https://ashutosh.us \\
github.com/2727-ask \\
\today
\end{flushleft}

\vspace{0.5em}

\textbf{Hiring Manager} \\
Cloudflare \\

\vspace{1em}

Dear Hiring Manager,

I am excited to apply for the **Software Engineer Intern (Summer 2025)** position at Cloudflare. As a Master's student in Software Engineering at Arizona State University and an experienced full-stack developer, I am eager to contribute my expertise in scalable systems, distributed architectures, and modern web technologies to Cloudflare’s mission of building a better Internet.

With over three years of experience in software development, including my tenure at **Western Union**, I have worked on high-impact projects such as the **migration of WUPOS from Apache Tapestry to Angular 14**, leading to a **15\% increase in revenue** and an enhanced user experience. Additionally, I developed an internal **Point of Sale Development Utility** that improved developer efficiency by **70\%**. My background in cloud computing, containerization, and microservices is further demonstrated by my work at **MindsClik Digital Solutions**, where I deployed microservices on **Google Cloud Platform using Kubernetes** and introduced **Flutter for cross-platform development**.

Cloudflare's commitment to improving Internet security, performance, and reliability resonates strongly with me. My projects, such as an **Online Compiler Web IDE** leveraging **Docker, Kubernetes, and Redis**, demonstrate my ability to design scalable architectures that support high availability and performance—values that align with Cloudflare’s global network infrastructure. Furthermore, my experience in developing **serverless architectures using AWS Lambda** and optimizing real-time systems with **WebRTC and Redis** positions me well to contribute to Cloudflare’s engineering challenges.

I am highly motivated to work in a fast-paced, collaborative environment where I can leverage my skills in **Go, Rust, Python, and TypeScript** to build secure and high-performance applications. I am eager to learn from Cloudflare’s experienced engineers while contributing to impactful projects that reach millions of users worldwide.

I welcome the opportunity to discuss how my technical background and problem-solving skills align with Cloudflare’s goals. Thank you for your time and consideration—I look forward to the possibility of joining your team this summer.

Sincerely, \\
Ashutosh Kumbhar

\end{document}
