\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}
\begin{document}

\begin{flushleft}
\textbf{Ashutosh Kumbhar} \\
Tempe, Arizona, USA \\
+1 623-698-7433 \\
akumbha3@asu.edu \\
https://ashutosh.us \\
github.com/2727-ask \\
\today
\end{flushleft}
\vspace{0.5em}
\textbf{Hiring Manager} \\
BMO U.S.
\vspace{1em}

Dear Hiring Manager,

I am writing to express my interest in the Software Developer Internship for Summer 2025 at BMO U.S. With a strong background in software engineering, including hands-on experience in developing scalable applications, cloud computing, and microservices, I am eager to contribute to BMO's dynamic team. My academic pursuits, combined with my professional experiences, have equipped me with the skills to thrive in a fast-paced, collaborative environment.

During my tenure at Western Union, I contributed to a 15\% revenue increase by migrating the WUPOS application from Apache Tapestry to Angular 14. Additionally, I developed tools that boosted developer efficiency by 70\%, showcasing my proficiency in application integration and system development. My work also involved implementing Test-Driven Development (TDD) strategies, reinforcing my understanding of the software development lifecycle.

I am particularly drawn to BMO's focus on creative thinking, adaptability, and fostering a culture of continuous learning. These values resonate deeply with my approach to software development. My experience working with cloud platforms, particularly Google Cloud and AWS, aligns with your cloud computing needs. I am confident in my ability to adapt to new technologies and quickly integrate into your development processes.

I am excited about the opportunity to contribute to BMO’s technology-driven projects while learning from a team that values innovation and problem-solving. I would welcome the chance to further discuss how my skills align with your needs.

Sincerely, \\
Ashutosh Kumbhar

\end{document}
