\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}

\begin{document}

\begin{flushleft}
\textbf{Ashutosh Kumbhar} \\
Tempe, Arizona, USA \\
+1 623-698-7433 \\
akumbha3@asu.edu \\
https://ashutosh.us \\
github.com/2727-ask \\
\today
\end{flushleft}

\vspace{0.5em}

\textbf{Hiring Manager} \\
ASU IT \\

\vspace{1em}

Dear Hiring Manager,

I am a Master's student in Software Engineering at Arizona State University with a robust background in full-stack development and software engineering. I am eager to apply for the IT Grader position at ASU IT, where my technical expertise and collaborative mindset align seamlessly with the department's commitment to advancing education and innovation.

Throughout my professional journey, I have honed my technical and interpersonal skills. At Western Union, I enhanced developer efficiency by 70\% through the creation of a Point of Sale Development Utility and contributed to modernizing the company’s infrastructure, resulting in a 15\% revenue increase. My hands-on experience with cutting-edge technologies, including Angular, Docker, Kubernetes, and cloud platforms, has equipped me to manage complex, time-sensitive tasks effectively.

Beyond technical contributions, I am deeply committed to fostering student success, a core value shared by ASU IT. My role as a team leader at LinkCode Technologies, where I managed a team of 10 developers, emphasized mentorship and collaboration, qualities essential for supporting students during office hours and class activities. Moreover, my experience creating scalable systems and ensuring the timely completion of deliverables directly complements the grading and course management responsibilities of this role.

ASU IT’s mission to create a world-class learning experience resonates with me. I am inspired by the organization's emphasis on interdisciplinary research and its dedication to fostering inclusive communities. Joining your team would allow me to contribute to this vision while leveraging my technical expertise and passion for education.

I am confident that my blend of technical proficiency, leadership experience, and dedication to student success makes me a strong fit for the IT Grader position. I would welcome the opportunity to discuss how my background and goals align with ASU IT’s objectives. Thank you for considering my application.

Sincerely, \\
Ashutosh Kumbhar

\end{document}
