\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}

\begin{document}

\begin{flushleft}
\textbf{Ashutosh Kumbhar} \\
Tempe, Arizona, USA \\
+1 623-698-7433 \\
akumbha3@asu.edu \\
linkedin.com/in/ashutosh-kumbhar \\
github.com/2727-ask \\
\today
\end{flushleft}

\vspace{0.5em}

\textbf{Hiring Manager} \\
\textbf{FireSeeds} \\

\vspace{1em}

Dear Hiring Manager,

I am excited to apply for the Software Engineering Intern position at FireSeeds. As a Master's student in Software Engineering at Arizona State University with a robust background in software development, I am eager to contribute my technical expertise and collaborative skills to your mission of delivering impactful SaaS solutions.

During my tenure at Western Union, I enhanced developer efficiency by 70\% through the creation of a Point of Sale Development Utility and contributed to the migration of their POS system, leading to a 15\% revenue increase. My experience includes building scalable cloud solutions at MindsClik Digital Solutions, where I deployed microservices on Google Cloud Platform, and leading the design of a Learning Management System at LinkCode Technologies, resulting in a 35\% revenue boost. These roles have honed my abilities in full-stack development, debugging, and collaborative problem-solving.

FireSeeds' emphasis on leadership development and integrity aligns closely with my passion for creating technology that drives meaningful change. I am proficient in the technologies and frameworks mentioned in the job description, including Angular, JavaScript, SQL, and cloud environments. My experience with object-oriented programming and tools like Git and Jira makes me well-prepared to contribute effectively to your team.

I am particularly drawn to FireSeeds' culture of fostering growth and development, as it resonates with my own commitment to lifelong learning. With my proven track record in designing and delivering high-impact software solutions, I am confident in my ability to excel as part of your innovative team.

I look forward to the opportunity to discuss how my skills and experiences align with FireSeeds' vision. Thank you for considering my application.

Sincerely, \\
Ashutosh Kumbhar

\end{document}
