\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}

\begin{document}

\begin{flushleft}
\textbf{Ashutosh Kumbhar} \\
Tempe, Arizona, USA \\
+1 623-698-7433 \\
akumbha3@asu.edu \\
https://ashutosh.us \\
github.com/2727-ask \\
\today
\end{flushleft}

\vspace{0.5em}

\textbf{Hiring Manager} \\
ASU PROJECT ASSISTANT \\

\vspace{1em}

Dear Hiring Manager,

I am writing to express my interest in the Project Assistant position at ASU. Currently pursuing a Master's in Software Engineering at Arizona State University, I bring a blend of technical expertise, organizational skills, and a passion for precision that aligns closely with the requirements of this role. My career goal is to contribute to initiatives that emphasize meticulous documentation, efficient data organization, and meaningful impact in academia or research settings.

During my tenure as a Software Developer at Western Union, I enhanced developer efficiency by 70\% through tool development and spearheaded a migration project that improved system usability and increased revenue by 15\%. These experiences honed my attention to detail and adaptability—qualities crucial for formatting manuscripts, creating structured data, and adhering to specific publishing guidelines.

I am proficient in Microsoft Office, including Word, Excel, and PowerPoint, and have experience working with design tools like Adobe Photoshop and Illustrator. For instance, I deployed entire microservice infrastructures using Kubernetes and Docker, showcasing my capability to manage large-scale organizational tasks efficiently. Additionally, my work on diverse projects, such as developing a Diagnostic Center Resource Management System, highlights my ability to organize and process data for archiving purposes.

I am particularly drawn to the emphasis on archiving field data and creating accurate, structured deliverables in this role. ASU’s commitment to fostering impactful research resonates deeply with my values of innovation and precision. While I do not have professional experience in archaeology, my academic curiosity and technical acumen equip me to excel in tasks requiring the synthesis of complex datasets and the meticulous preparation of documents.

I would welcome the opportunity to discuss how my skills and experiences align with your team's needs. Thank you for considering my application, and I look forward to the possibility of contributing to ASU's mission.

Sincerely, \\
Ashutosh Kumbhar

\end{document}
