\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}

\begin{document}

\begin{flushleft}
\textbf{Ashutosh Kumbhar} \\
Tempe, Arizona, USA \\
+1 623-698-7433 \\
akumbha3@asu.edu \\
https://ashutosh.us \\
github.com/2727-ask \\
\today
\end{flushleft}

\vspace{0.5em}

\textbf{Hiring Manager} \\
ST Engineering iDirect \\

\vspace{1em}

Dear Hiring Manager,

I am excited to apply for the Software Engineering Intern position at ST Engineering iDirect. As a Master’s student in Software Engineering at Arizona State University, graduating in August 2024, I bring a strong foundation in software development and a proven ability to deliver impactful solutions. My passion for technology aligns with your mission to revolutionize satellite communications and create groundbreaking opportunities in global connectivity.

During my tenure as a Software Developer at Western Union, I enhanced developer efficiency by 70\% through the creation of a custom Point of Sale Development Utility and contributed to a 15\% revenue increase by migrating a core application to Angular 14. At MindsClik Digital Solutions, I spearheaded the integration of Flutter as a new application stack, boosting application performance and scalability. These experiences honed my skills in Java, Python, and Agile methodologies, directly aligning with the qualifications outlined for this role.

What excites me most about ST Engineering iDirect is your commitment to next-generation solutions for broadband IP networking via satellite. I share your passion for addressing economic and technological challenges and have demonstrated a similar drive in my academic and professional projects. For instance, I developed an Online Compiler Web IDE using Docker and Kubernetes, optimizing resource management while supporting over ten programming languages, showcasing my expertise in scalable and distributed systems.

I am eager to collaborate with your talented team of engineers to design, implement, and test software solutions. My background in Test-Driven Development (TDD) and experience with version control systems such as Git will enable me to contribute effectively to your agile and collaborative environment.

Thank you for considering my application. I am enthusiastic about the opportunity to bring my skills and passion for technology to ST Engineering iDirect and would welcome the chance to discuss how I can contribute to your innovative projects.

Sincerely, \\
Ashutosh Kumbhar

\end{document}
