\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}

\begin{document}

\begin{flushleft}
\textbf{Ashutosh Kumbhar} \\
Tempe, Arizona, USA \\
+1 623-698-7433 \\
akumbha3@asu.edu \\
https://ashutosh.us \\
github.com/2727-ask \\
\today
\end{flushleft}

\vspace{0.5em}

\textbf{Hiring Manager} \\
ASU-GRADER \\

\vspace{1em}

Dear Hiring Manager,

I am writing to express my interest in the position of Grader for HSE, GIT, EGR, AMT, ERM, IT, and TEM at ASU's Ira A. Fulton Schools of Engineering. As a current master’s student in Software Engineering at Arizona State University with a robust academic and professional background, I am eager to contribute to the outstanding learning experiences and innovative culture at Fulton Engineering.

My academic journey and professional experiences have honed my technical, organizational, and interpersonal skills. Having served as a Software Developer at Western Union, I led the development of a Point of Sale Development Utility, boosting developer efficiency by 70\%, and contributed to migrating systems that enhanced user experience and increased revenue by 15\%. My ability to deliver timely results aligns with the grading role's requirement for efficiency and accuracy.

In my role as a Full-Stack Developer at LinkCode Technologies, I managed a team of 10 developers and implemented CI/CD pipelines, improving workflows and fostering collaboration. These experiences underscore my aptitude for clear communication, attention to detail, and adaptability—skills critical for grading assignments, assisting students, and maintaining course materials on Blackboard.

The Fulton Schools of Engineering's emphasis on interdisciplinary innovation and fostering diversity resonates deeply with me. I am passionate about creating inclusive learning environments and supporting academic excellence, values I have consistently upheld in my professional and academic endeavors.

I am excited about the prospect of contributing to ASU’s commitment to excellence in research and education. I look forward to the opportunity to discuss how my background and skills align with this role's requirements and the mission of the Fulton Schools of Engineering.

Thank you for considering my application. I welcome the opportunity for further discussion and am available at your earliest convenience.

Sincerely, \\
Ashutosh Kumbhar

\end{document}
