\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}
\begin{document}

\begin{flushleft}
\textbf{Ashutosh Kumbhar} \\
Tempe, Arizona, USA \\
+1 623-698-7433 \\
akumbha3@asu.edu \\
\url{https://ashutosh.us} \\
\url{github.com/2727-ask} \\
\today
\end{flushleft}

\vspace{0.5em}

\textbf{Hiring Manager} \\
Amazon \\

\vspace{1em}

Dear Hiring Manager,

I am excited to apply for the Software Development Engineer Internship at Amazon. As a Master's student in Software Engineering at Arizona State University, I bring a strong foundation in computer science, extensive industry experience, and a passion for solving complex problems to build scalable, efficient software solutions.

During my tenure at Western Union, I contributed to the development of a Point of Sale (POS) utility that enhanced developer efficiency by 70\%, and led the migration of WUPOS to Angular 14, resulting in a 15\% revenue increase. These experiences honed my proficiency in technologies like Angular, Node.js, and Test-Driven Development (TDD). My entrepreneurial contributions at MindsClik included creating a white-labeled e-commerce solution and deploying microservice architectures on Google Cloud Platform, further strengthening my expertise in backend and cloud technologies.

Amazon's commitment to innovation and its mission to "define tomorrow" resonates deeply with my career aspirations. I am particularly inspired by the company's focus on distributed systems and scalable technologies, areas I explored while designing a cloud-based online compiler platform with Kubernetes and QEMU during my academic projects. My ability to articulate complex technical challenges and drive solutions would allow me to contribute effectively to Amazon's dynamic teams.

My technical skill set spans modern programming languages like Java, Python, and C++, alongside experience in distributed systems, relational databases, and optimization techniques. I thrive in collaborative, fast-paced environments and bring a proven track record of delivering impactful solutions through internships and professional roles.

I am eager to bring my problem-solving skills, technical expertise, and passion for innovation to Amazon's team. I would welcome the opportunity to discuss how my experiences align with your objectives and look forward to contributing to Amazon’s vision for the future.

Sincerely, \\
Ashutosh Kumbhar

\end{document}
