\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}

\begin{document}

\begin{flushleft}
\textbf{Ashutosh Kumbhar} \\
Tempe, Arizona, USA \\
+1 623-698-7433 \\
akumbha3@asu.edu \\
https://ashutosh.us \\
github.com/2727-ask \\
\today
\end{flushleft}

\vspace{0.5em}

\textbf{Hiring Manager} \\
Cambridge Mobile Telematics \\

\vspace{1em}

Dear Hiring Manager,

I am excited to apply for the Software Engineering Intern position on the Platform Applications team at Cambridge Mobile Telematics (CMT). As a Master’s student in Software Engineering at Arizona State University, I am eager to contribute to your mission of enhancing road safety through innovative telematics solutions.

Throughout my academic and professional journey, I have honed skills that align closely with CMT's objectives. At Western Union, I played a pivotal role in enhancing the WUPOS retail application, notably developing a utility that improved developer efficiency by 70\%. Additionally, I contributed to a major front-end migration project that boosted revenue by 15\%, demonstrating my ability to manage complex system integrations effectively. My work in cloud technologies, including deploying microservices on Kubernetes and Google Cloud Platform, further underscores my expertise in creating scalable and reliable solutions.

CMT's AI-driven DriveWell\textsuperscript{\textregistered} Fusion platform resonates deeply with my passion for leveraging technology to solve real-world problems. My experience developing a cloud-based online compiler using Docker and Kubernetes reflects my capability to manage end-to-end platform integrations and optimize system performance. I am particularly drawn to the opportunity to collaborate on projects that enhance the Fusion Platform’s scalability and developer-friendliness, aligning with my commitment to innovation and excellence.

I am proficient in Python, Java, and several modern frameworks, including Angular and Vue.js. My experience in test-driven development and debugging complex systems equips me to identify and address challenges efficiently. At CMT, I am eager to bring this skill set to contribute meaningfully to the team’s success.

Thank you for considering my application. I am excited about the opportunity to join CMT in its mission to make roads safer and would welcome the chance to discuss how my skills and experiences align with your needs. I look forward to the possibility of contributing to your impactful work.

Sincerely, \\
Ashutosh Kumbhar

\end{document}
