\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}

\begin{document}

\begin{flushleft}
\textbf{Ashutosh Kumbhar} \\
Tempe, Arizona, USA \\
+1 623-698-7433 \\
akumbha3@asu.edu \\
https://ashutosh.us \\
github.com/2727-ask \\
\today
\end{flushleft}

\vspace{0.5em}

\textbf{Hiring Manager} \\
ASU Chandler Innovation Center \\

\vspace{1em}

Dear Hiring Manager,

I am writing to express my interest in the part-time Event and Operations Coordinator role at the ASU Chandler Innovation Center. As a graduate student in Software Engineering at Arizona State University, I am excited about the opportunity to contribute my organizational skills and technical expertise to support the center's operations and mission.

Throughout my career, I have honed my ability to manage complex projects and work collaboratively in dynamic environments. As a Software Developer at Western Union, I spearheaded the development of tools that improved efficiency by 70\% and facilitated a seamless migration to modern platforms, directly increasing revenue by 15\%. In addition, my experience leading teams and implementing scalable solutions in previous roles has equipped me with the communication and leadership skills necessary for providing exceptional support to events and operations.

The ASU Chandler Innovation Center’s commitment to fostering collaboration and innovation resonates deeply with me. Having organized and participated in various technical and professional events, I understand the importance of creating an inclusive and well-organized environment for diverse stakeholders. My experience with tools like Smartsheets, combined with a proactive approach to problem-solving, ensures that I can efficiently manage tasks such as event coordination, front desk coverage, and operational support.

I am particularly drawn to the flexibility and hands-on nature of this role, aligning well with my schedule and skills. My ability to adapt quickly to new challenges and my dedication to upholding organizational values make me confident in my ability to excel in this position.

Thank you for considering my application. I would welcome the opportunity to discuss how my background and skills align with the needs of the ASU Chandler Innovation Center. I look forward to contributing to the success of your events and operations.

Sincerely, \\
Ashutosh Kumbhar

\end{document}
