\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}

\begin{document}

\begin{flushleft}
\textbf{Ashutosh Kumbhar} \\
Tempe, Arizona, USA \\
+1 623-698-7433 \\
akumbha3@asu.edu \\
linkedin.com/in/ashutosh-kumbhar \\
github.com/2727-ask \\
\today
\end{flushleft}

\vspace{0.5em}
\textbf{Hiring Manager} \\
Riot Platforms \\

\vspace{1em}

Dear Hiring Manager,

I am writing to express my interest in the Software Engineering Intern position at Riot Platforms, as advertised. With a strong foundation in software development, demonstrated through my work with companies like Western Union and LinkCode Technologies, I am eager to contribute to your team and further develop my skills in the Bitcoin and digital infrastructure space. Currently pursuing my Master’s in Software Engineering at Arizona State University, I am excited about the opportunity to immerse myself in an innovative, collaborative environment like Riot's.

I bring hands-on experience in a variety of software development projects, including my work in migrating systems to modern frameworks, such as transitioning Western Union’s retail application to Angular 14, which resulted in a 15\% increase in revenue. My technical skills in languages like Java, Python, and JavaScript, coupled with my experience in Agile environments, would allow me to contribute effectively to the team. At LinkCode, I designed and implemented a learning management system that boosted organizational revenue by 35\%, and I have built several full-stack applications leveraging frameworks such as Angular, React, and Django.

Riot’s mission to innovate in the Bitcoin mining and digital infrastructure sector is particularly exciting to me. I am passionate about Bitcoin, and I look forward to leveraging my technical background to contribute to Riot’s growth. The opportunity to work with a forward-thinking company like Riot aligns with my values of creativity, problem-solving, and continuous learning.

Thank you for considering my application. I am confident that my skills and enthusiasm make me a strong fit for this internship. I look forward to discussing how I can contribute to the continued success of Riot Platforms.

Sincerely, \\
Ashutosh Kumbhar

\end{document}
