\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}
\begin{document}

\begin{flushleft}
\textbf{Ashutosh Kumbhar} \\
Tempe, Arizona, USA \\
+1 623-698-7433 \\
akumbha3@asu.edu \\
https://ashutosh.us \\
github.com/2727-ask \\
\today
\end{flushleft}

\vspace{0.5em}

\textbf{Hiring Manager} \\
Evolv \\

\vspace{1em}

Dear Hiring Manager,

I am excited to apply for the Web App Development Intern (Summer '25) position at Evolv. As a graduate student in Software Engineering at Arizona State University and a full-stack developer with over four years of experience, I am eager to contribute to Evolv’s mission of innovation and excellence in cutting-edge technology solutions.

In my previous role at Western Union, I collaborated on migrating their legacy Point of Sale system to Angular 14, achieving a 15\% increase in revenue and significantly improving user experience. My ability to develop intuitive user interfaces aligns with Evolv’s emphasis on designing impactful UX. Additionally, I built a white-labeled e-commerce solution at MindsClik Digital Solutions, showcasing my versatility in web development and problem-solving aptitude.

Your focus on machine vision workflows and technical skills like React and REST APIs resonate deeply with my background. For example, I developed a cloud-based online compiler supporting over 10+ programming languages using Docker and Kubernetes, enhancing scalability and system reliability. Similarly, at LinkCode Technologies, I integrated WebRTC for real-time communication in a Learning Management System, reflecting my ability to implement and optimize cutting-edge technologies.

What excites me most about Evolv is the opportunity to work within a dynamic, fast-paced team that prioritizes innovation and problem-solving. Your approach to leadership, which empowers teams to synthesize and implement solutions independently, aligns with my proactive work ethic and adaptability. I am confident that my technical expertise, combined with a results-driven mindset, would make me an asset to your team.

I welcome the opportunity to discuss how my experience and skills can contribute to Evolv’s mission. Thank you for considering my application, and I look forward to the possibility of contributing to your team.

Sincerely, \\
Ashutosh Kumbhar

\end{document}
