\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}

\begin{document}

\begin{flushleft}
\textbf{Ashutosh Kumbhar} \\
Tempe, Arizona, USA \\
+1 623-698-7433 \\
akumbha3@asu.edu \\
https://ashutosh.us \\
github.com/2727-ask \\
\today
\end{flushleft}

\vspace{0.5em}

\textbf{Hiring Manager} \\
PayPal \\

\vspace{1em}

Dear Hiring Manager, 

I am excited to apply for the Backend Software Engineer Intern position at PayPal. With a Master's in Software Engineering from Arizona State University (in progress) and over three years of experience in software development, I bring a solid foundation in backend technologies and a proven track record of delivering scalable, high-performance solutions.

In my most recent role at Western Union, I contributed to migrating the Point of Sale system to Angular 14, resulting in a 15\% revenue increase and improved user experience. Additionally, I developed a utility tool that enhanced developer efficiency by 70\%. My experience extends to cloud-based solutions, where I deployed microservices on Google Cloud Platform and implemented serverless architectures with AWS Lambda. My technical expertise spans languages like Python, Java, and Node.js, and frameworks such as Django and Express.js, making me well-suited to design and optimize backend services at PayPal.

I am particularly drawn to PayPal's mission of democratizing financial services and fostering global economic inclusivity. The company's innovative approach to enabling seamless, secure transactions aligns with my values of creating impactful technology solutions. I am eager to contribute to PayPal's efforts in developing distributed systems that power its global payment platform, leveraging my skills in REST APIs, database optimization, and scalable software design.

At PayPal, I am confident in my ability to tackle complex technical challenges and collaborate effectively with cross-functional teams to drive innovation. I am excited to bring my problem-solving skills, technical acumen, and passion for technology to a company that values inclusion, collaboration, and wellness.

Thank you for considering my application. I welcome the opportunity to discuss how my skills and experiences align with PayPal's goals. I look forward to contributing to your team’s success.

Sincerely, \\
Ashutosh Kumbhar

\end{document}
