\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}

\begin{document}

\begin{flushleft}
\textbf{Ashutosh Kumbhar} \\
Tempe, Arizona, USA \\
+1 623-698-7433 \\
akumbha3@asu.edu \\
\texttt{https://ashutosh.us} \\
\texttt{github.com/2727-ask} \\
\today
\end{flushleft}

\vspace{0.5em}

\textbf{Hiring Manager} \\
Pure Storage \\

\vspace{1em}

Dear Hiring Manager,

I am thrilled to apply for the Software Engineer Intern position for Summer 2025 at Pure Storage. As a Master's student in Software Engineering at Arizona State University, I am eager to contribute to Pure's mission of empowering innovators by simplifying how people consume and interact with data. Your vision resonates deeply with my passion for leveraging technology to drive meaningful impact.

In my role as a Software Developer at Western Union, I spearheaded the migration of a legacy point-of-sale system to Angular 14, leading to a 15\% revenue increase and significant improvements in user experience. Additionally, I developed a Test-Driven Development (TDD) strategy using the Playwright framework, ensuring robust, scalable applications. My experience designing and implementing CI/CD pipelines and optimizing resource management with Kubernetes has honed my skills in building scalable, high-performance systems—qualities essential for success at Pure Storage.

Pure's emphasis on redefining the storage experience and its customer-centric approach align perfectly with my values. I am particularly drawn to the company's innovative culture and its consistent recognition as a leader in the industry, including being named a leader in the Magic Quadrant for ten consecutive years.

With a solid foundation in C++, Python, and Go, coupled with my experience in cross-functional collaboration and problem-solving, I am confident in my ability to contribute to Pure's cutting-edge projects. My technical skills, combined with a deep understanding of object-oriented programming and operating systems, equip me to excel in this role.

I look forward to the opportunity to bring my skills and passion to Pure Storage. Thank you for considering my application. I am excited about the prospect of contributing to your mission and would welcome the chance to discuss how my background aligns with your needs.

Sincerely, \\
Ashutosh Kumbhar

\end{document}
