\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}


\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}


\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]


\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small#1} & \textbf{\small#2} \\
      \textit{\small#3} & \textit{\small#4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}




\begin{document}

\begin{center}
    \textbf{\Huge \scshape Ashutosh Kumbhar} \\ \vspace{1pt}
    \small +1 623-698-7433 $|$ \href{mailto:akumbha3@asu.edu}{\underline{akumbha3@asu.edu}} $|$ 
    \href{https://ashutosh.us}{\underline{https://ashutosh.us}} $|$
    \href{https://github.com/2727-ask}{\underline{github.com/2727-ask}} $|$
    {\underline{Tempe, Arizona, USA}}
\end{center}




\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Developer}{August 2023 -- August 2024}
      {Western Union}{Full-Time}
      \resumeItemListStart
        \resumeItem{Contributed to developing and maintaining the Western Union POS retail application, ensuring seamless functionality and performance.}
        \resumeItem{Developed \textbf{Point Of Sale Development Utility}, which boosted developer \textbf{efficiency by 70\%}.
}
        \resumeItem{Collaborated in the migration of \textbf{WUPOS} from Apache Tapestry to Angular 14, resulting in \textbf{a 15\% increase in revenue}, significant improvements in both agent and user experience, and \textbf{expanded market share} through modernized front-end architecture.}
        \resumeItem{Executed a Test-Driven Development (TDD) strategy within teams using the \textbf{Playwright} framework.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer}{June 2022 -- February 2023}
      {MindsClik Digital Solutions}{Part-Time}
      \resumeItemListStart
        \resumeItem{Developed a white-labeled e-commerce solution, which evolved into a \textbf{core product} offering.
}
        \resumeItem{Introduced and integrated \textbf{Flutter} as a new application stack, resulting in enhanced performance and increased development productivity.}
    \resumeItemListEnd

      \resumeSubheading
      {Full-Stack Developer}{January 2021 -- June 2022}
      {LinkCode Technologies}{Part-Time}
      \resumeItemListStart
        \resumeItem{Designed the architecture for the LinkCode LMS, driving the organization's digital transformation and resulting in a \textbf{35\% increase in revenue}.}
        \resumeItem{Managed a team of \textbf{10 developers}, overseeing the collective development and implementation of the software.}
        \resumeItem{Migrated the entire infrastructure to a server-less architecture using AWS \textbf{Lambda}, enhancing scalability and cost-efficiency.}
        \resumeItem{Implemented \textbf{Web-RTC} for video conferencing, improving real-time communication capabilities.}
        \resumeItem{Established CI/CD pipelines with Jenkins, optimizing development workflows and deployment processes.}
      \resumeItemListEnd

      \resumeSubheading
      {Full-Stack Development Intern}{April 2020 -- September 2020}
      {Aitheon}{Internship}
      \resumeItemListStart
        \resumeItem{Created a \textbf{no-code} application development platform using Visual Studio Web, Node.js, Node-RED, and Vue.js, enabling users to create applications without traditional coding.}
        \resumeItem{Development of \textbf{IoT} applications leveraging Robot Operating Systems, NVIDIA Jetson Nano, and Code-Studio.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd



\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading
  {\textbf{Online Compiler Web IDE} $|$ \emph{Docker, Kubernetes, Redis, Node.js, Angular, Nginx}}{}
\resumeItemListStart
  \resumeItem{Developed a cloud-based platform supporting over 10+ programming languages, enabling software developers and students to perform heavy computation without local hardware.}
  \resumeItem{Optimized resource management by deploying an in-house bare-metal server using QEMU and Ngrok, reducing infrastructure costs and increasing system reliability.}
  \resumeItem{Collaborated with a team to design a highly scalable architecture leveraging containerization technologies like Docker and Kubernetes.}
  \resumeItem{Improved user experience and streamlined development by implementing CI/CD pipelines and integrating real-time collaboration features.}
\resumeItemListEnd
\resumeProjectHeading
  {\textbf{Diagnostic Center Resource Management System} $|$ \emph{Vue.js, Electron.js, Firebase, GCP}}{}
\resumeItemListStart
  \resumeItem{Designed and implemented a web application to manage resources and patient data, boosting productivity by \textbf{80\%} for the Unique Diagnostic Center.}
  \resumeItem{Integrated Firebase for real-time data synchronization and GCP for cloud-based resource scaling, improving performance and availability.}
  \resumeItem{Built user-friendly frontend using Vue.js, focusing on responsive design and cross-platform compatibility via Electron.js.}
  \resumeItem{Collaborated in Agile sprints to deliver regular updates and features, ensuring continuous improvement and meeting user requirements.}
\resumeItemListEnd
\resumeProjectHeading
  {\textbf{Hospital Management System} $|$ \emph{Django, AWS, REST, PostgreSQL}}{}
\resumeItemListStart
  \resumeItem{Engineered an emergency resource management system to track real-time availability of hospital beds, vaccines, and ventilators during the COVID-19 pandemic.}
  \resumeItem{Implemented RESTful APIs using Django, providing efficient data handling and integration with AWS EC2 for scalable cloud hosting.}
  \resumeItem{Collaborated with healthcare professionals to design intuitive dashboards, making critical information accessible to non-technical users.}
  \resumeItem{Ensured data integrity and security by incorporating PostgreSQL for robust database management and encryption.}
\resumeItemListEnd
\resumeProjectHeading
  {\textbf{JSON to TypeScript Converter} $|$ \emph{JavaScript, HTML5}}{}
\resumeItemListStart
  \resumeItem{Developed an algorithm from scratch to detect and convert nested JSON objects into corresponding TypeScript interfaces, simplifying the workflow for developers.}
  \resumeItem{Built the application using Vanilla JavaScript for high compatibility across different browsers without relying on external libraries.}
  \resumeItem{Enhanced user experience by incorporating real-time validation and error checking, reducing manual effort and preventing conversion errors.}
  \resumeItem{Collaborated with users to gather feedback and iteratively improve the user interface, delivering a more intuitive tool.}
\resumeItemListEnd
\resumeProjectHeading
  {\textbf{Crypto Tracker} $|$ \emph{Flutter, FlutterFlow, Dart, Firebase, Cloud Firestore}}{}
\resumeItemListStart
  \resumeItem{Developed a real-time cryptocurrency price tracker using Flutter and Dart, scraping live data via Gecko API and web scraping techniques.}
  \resumeItem{Stored historical price data in Cloud Firestore and displayed candlestick charts for users to visualize trends and patterns.}
  \resumeItem{Implemented responsive UI using FlutterFlow, ensuring seamless performance across devices and platforms.}
  \resumeItem{Collaborated with a team to integrate Firebase for user authentication and cloud-based data storage, providing a secure and scalable backend.}
\resumeItemListEnd
\resumeProjectHeading
  {\textbf{Instagram Video Scraper + Auto YouTube Shorts Uploader} $|$ \emph{Selenium, BS4, Flutter, FastAPI, GenAI}}{}
\resumeItemListStart
  \resumeItem{Developed a Python script to automatically scrape Instagram videos while scrolling through reels using Selenium and BeautifulSoup.}
  \resumeItem{Automated the uploading of videos to YouTube, including generating video tags and metadata using GenAI for improved search visibility.}
  \resumeItem{Built a cross-platform interface using Flutter, allowing users to configure scraping settings and monitor uploads in real-time.}
  \resumeItem{Integrated FastAPI to handle backend processes, optimizing task execution and performance.}
\resumeItemListEnd
\resumeSubHeadingListEnd


\section{Technical Skills}
\resumeSubHeadingListStart
  \resumeSubItem{\textbf{Languages:} C, C++, Java, Python, Dart, Go, JavaScript, Rust, HTML5.}
  \resumeSubItem{\textbf{Frameworks:} Angular, ReactJS, Vue.js, Django, Flask, Express.js, Electron.js, Tauri, Flutter, Ionic, Spring Boot.}
  \resumeSubItem{\textbf{Technologies:} Docker, Kubernetes, REST, JSON, TypeScript, GenAI, Selenium, BS4, FastAPI, Operating Systems.}
  \resumeSubItem{\textbf{Developer Tools:} Git, Docker, Google Cloud Platform, AWS, Firecracker, Kubernetes, QEMU, Redis, Agile, SCRUM, Linux, JIRA.}
  \resumeSubItem{\textbf{Database:} MongoDB, PostgreSQL, Oracle, MySQL, MariaDB, Firebase, D-Graph, SQLite.}
  \resumeSubItem{\textbf{Soft Skills:} Strong verbal and written communication, Initiative, Team collaboration, Deadline management.}
  \resumeSubItem{\textbf{Internship Requirements:} Currently enrolled in a BS, MS, or PhD program in Computer Science or a related field, Able to work full-time for 12 consecutive weeks, Open to working in an office environment.}
\resumeSubHeadingListEnd

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Masters in Software Engineering}{August 2024 -- Current}
      {Arizona State University}{}
    \resumeSubheading
      {Bachelors in Computer Science}{August 2019 -- July 2023}
      {Savitribai Phule Pune university}{}
  \resumeSubHeadingListEnd

\end{document}



